ML Estimation of Matrix t Distributions with Expectation Maximization

### 2016-11-23 paper.tex
Added author info and some minor changes.

\title{Estimation of Matrix-t distributions with Expectation
Maximization}

\author{Zahari Kassabov\thanks{TIF-UNIMI-2016-5}\\
        Dipartimento di Fisica, Universit\`a di Torino and INFN, Sezione di Torino\\
		TIF Lab, Dipartimento di Fisica, Universit\`a di Milano\\
        E-mail: \email{kassabov@to.infn.it}}

@@

\begin{abstract}
We derive the expectation-maximization (EM) formulae for
Matrix-$t$ distributions and discuss their practical implementation.
\end{abstract}

\paragraph{Introduction}
Matrix-$t$ distributions have been applied to several predictive
problems, such as spatial interpolation applied to the prediction of
pollution concentration, or recommendation systems \cite{NIPS2007_3203}???
...

@@

\begin{equation}
\int_{S>0}e^{-\textrm{tr}SA}(\det S)^{x}dS=\Gamma_{p}\left(\frac{1}{2}(1+p+2x)\right)(\det A)^{\frac{1}{2}(1+p+2x)}\label{eq:intmultgammadef}
\end{equation}
where we integrate $S$ over the space of positive definite $p\times p$
matrices, $A$ is a $p\times p$ nonsingular matrix, and the multivariate
gamma function $\Gamma_{p}(a)$ is given in terms of the standard
gamma function by:
\begin{equation}
\Gamma_{p}(a)=\pi^{p(p-1)/4}\prod_{j=1}^{p}\Gamma\left(a+(1-j)/2\right)\label{eq:multgammadef}
\end{equation}
we also define the multivariate digamma function
\[
\psi_{p}(a)=\frac{\partial}{\partial a}\log\Gamma_{p}(a)=\sum_{j=1}^{p}\psi(a+(1-j)/2)
\]

>>>>

\title{ML Estimation of Matrix t Distributions with Expectation Maximization}

\author{Zahari Kassabov\thanks{TIF-UNIMI-2016-5}\\
        Dipartimento di Fisica, Universit\`a di Torino and INFN, Sezione di Torino\\
		TIF Lab, Dipartimento di Fisica, Universit\`a di Milano\\
        E-mail: \email{kassabov@to.infn.it}\\
        \\
        Hsien-Ching Kao\\
        Wolfram Research, Inc.\\
		Champaign, Illinois 61820, USA\\
		E-mail: \email{sp000088@gmail.com}
		}

@@

\maketitle

\begin{abstract}
Matrix-$t$ distribution has applications in various areas of applied statistics, including recommendation systems, remote sensing, etc. In this article we provide an expectation-maximization (EM) formulae for Matrix-$t$ distributions and discuss their practical implementation.
\end{abstract}

\paragraph{Introduction}
Matrix-$t$ distributions have been applied to several predictive problems, such as spatial interpolation applied to the prediction of pollution concentration \cite{}, recommendation systems \cite{NIPS2007_3203},
...

@@

\begin{equation}
\int_{S\succ 0}e^{-\textrm{tr}SA}(\det S)^{x}dS=\Gamma_{p}\left(\frac{1}{2}(1+p+2x)\right)(\det A)^{\frac{1}{2}(1+p+2x)}\label{eq:intmultgammadef}
\end{equation}
where we integrate $S$ over the space of positive definite $p\times p$
matrices, $A$ is a $p\times p$ nonsingular matrix, and the multivariate
gamma function $\Gamma_{p}(a)$ is given in terms of the standard
gamma function by:
\begin{equation}
\Gamma_{p}(a)=\pi^{p(p-1)/4}\prod_{j=1}^{p}\Gamma\left(a+(1-j)/2\right)\label{eq:multgammadef}
\end{equation}
we also define the multivariate digamma function
\[
\psi_{p}(a)=\frac{\partial}{\partial a}\log\Gamma_{p}(a)=\sum_{j=1}^{p}\psi(a+(1-j)/2)
\]
